Trends of downward SDR in Thessaloniki

### 2023-05-05 Article.Rmd
Commit 2023-05-05 15:17

documentclass:  article
classoption:    a4paper,oneside
fontsize:       12pt
geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
link-citations: yes
colorlinks:     yes
urlcolor:       blue

>>>>

documentclass:  article
classoption:    a4paper,oneside
fontsize:       12pt
geometry:       "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
link-citations: yes
colorlinks:     yes
urlcolor:       blue
